---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# howzat

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mdsumner/howzat.svg?branch=master)](https://travis-ci.org/mdsumner/howzat)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mdsumner/howzat?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/howzat)
[![Codecov test coverage](https://codecov.io/gh/mdsumner/howzat/branch/master/graph/badge.svg)](https://codecov.io/gh/mdsumner/howzat?branch=master)
<!-- badges: end -->

The goal of howzat is to convert spatial objects to [WKT (Well-Known-Text) geometry format](https://en.wikipedia.org/wiki/Well-known_text_representation_of_geometry). 

WIP: supremely unuseable and untested for now. 

## Installation

You can install the  development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/howzat")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(howzat)


library(silicate)  ## just for data examples
library(sf)        ## just to verify the formatting

wkt(sfzoo$polygon)
wkt(sfzoo$polygon) == st_as_text(sfzoo$polygon)
wkt(st_sfc(sfzoo$multipolygon, sfzoo$multipolygon + 10))
wkt(st_sf(a = 1, g = st_sfc(sfzoo$multipolygon)))
wkt(sfzoo$multilinestring)
wkt(sfzoo$multilinestring) == st_as_text(sfzoo$multilinestring)
wkt(sfzoo$linestring)
wkt(sfzoo$linestring) == st_as_text(sfzoo$linestring)
wkt(sfzoo$multipoint)
wkt(sfzoo$multipoint) == st_as_text(sfzoo$multipoint)
wkt(sfzoo$point)
wkt(sfzoo$point) == st_as_text(sfzoo$point)


wkt(sfzoo$multipolygon)
wkt(sfzoo$multipolygon) == st_as_text(sfzoo$multipolygon)

```


---

Please note that the 'howzat' project is released with a
  [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
